%
% ----- copyright and title pages
%
\Title{Modeling of Active Aeroservoelastic Systems}
\Author{Anthony Su}
\Year{2023}
\Program{William E. Boeing Department of Aeronautics \& Astronautics}

\Chair{Eli Livne}{Professor}{William E. Boeing Department of Aeronautics \& Astronautics}
\Signature{Ed Habtour}

\copyrightpage

\titlepage

%
% ----- abstract
%
\setcounter{page}{-1}
\abstract{
This thesis demonstrates the synthesis and testing of a physics-based aeroservoelastic mathematical model for a flexible wind tunnel model. Ground vibration testing of the wind tunnel model is detailed herein. An aeroservoelastic mathematical model was synthesized for the wind tunnel model from a finite-element analysis and first principles. The wind tunnel model's structural dynamic, aerodynamic, and actuator models were coupled together into a linear time-invariant state-space model. The wind tunnel model's frequency response was measured experimentally at the University of Washington's 3x3 low-speed wind tunnel. The frequency response was used to adjust the mathematical model to account for physical phenomena which were not well captured by the initial model. Results show that the updated mathematical model is able to capture the relevant physics and responses of the wind tunnel model. The results of this study can be used as the baseline for further system identification or for aeroservoelastic control law design.

}
 
%
% ----- contents & etc.
%
\tableofcontents
\listoffigures
\listoftables
 
%
% ----- glossary 
%
\chapter*{Nomenclature}
\addcontentsline{toc}{chapter}{Nomenclature}
\thispagestyle{plain}
%
{\renewcommand\arraystretch{1.0}
\noindent\begin{longtable}{@{}l @{\quad=\quad} l@{}}
\multicolumn{2}{@{}l}{\textbf{Notation}} \\
    $[\quad]$   & matrix \\
    $\{\quad\}$ & column vector \\

\multicolumn{2}{@{}l}{\textbf{Abbreviations}} \\
    CZT         & chirp Z-transform \\
    DFT         & discrete Fourier transform \\
    FEM         & finite element model \\
    FRF         & frequency response function \\
    GLA         & gust load alleviation \\
    GVT         & ground vibration testing \\
    HIL         & hardware-in-the-loop \\
    LE          & leading edge \\
    MARGE       & Model for Aeroelastic Response to Gust Excitation \\
    ODE         & ordinary differential equation \\
    % RFA         & rational function approximation \\
    SISO        & single-input single-output \\
    TE          & trailing edge \\
    
\multicolumn{2}{@{}l}{\textbf{Variables}} \\
% SCALARS
    $b$         & reference semi-chord \\
    $j$         & imaginary unit \\
    $k$         & reduced frequency \\
    $N_s$       & \# of elastic modes available \\
    $n_s$       & \# of elastic modes used in modeling \\
    $n_c$       & \# of rigid-body modes used in modeling \\ 
    $n_\text{lag}$ & \# of lag terms used in modeling \\
    $q_D$       & dynamic pressure \\
    $s$         & Laplace variable \\
    $U$         & airspeed \\
    $\omega$    & frequency \\
% VECTORS
%    $\{q\}$     & structural dynamic state \\
%    $\{r\}$     & aerodynamic lag state \\
%    $\{u\}$     & input \\
%    $\{x\}$     & plant state \\
%    $\{y\}$     & output \\
    
% MATRICES
%	$[A]$       &  \\
%	$[B]$       &  \\
%	$[C]$       &  \\
%	$[D]$       &  \\
%   $[I]$       & identity matrix \\
    
\multicolumn{2}{@{}l}{\textbf{Subscripts}} \\
    $s$         & structural (flexible) component \\
    $c$         & control (rigid) component \\
    $p$         & plant \\
    act         & actuator \\
    sens        & sensor
    
\end{longtable}}
 
%
% ----- acknowledgments
%
\acknowledgments{
I must first and foremost thank Professor Eli Livne for his mentorship and support throughout my foray into aeroservoelasticity. His passion for aeronautics has proven to be contagious and for that I am grateful.
I would like to thank colleagues John Berg and Eddie Ting for their enduring patience and readiness to lend experience.
Thanks also to Professor Marat Mor for his invaluable expertise and assistance in finite-element modeling; this work would not have been possible without him.
Thanks to the members of the UW Illimited lab for generously lending me their equipment.
Finally, I would like to thank all of the colleagues, friends, and family who have walked alongside me throughout my educational journey.
}

%
% ----- dedication
%
%\dedication{\begin{center}to Lorem Ipsum, my dear friend\end{center}}

%
% end of the preliminary pages